---
title: "FiTnEss -- Identifying essential genes from TnSeq data"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    toc: true
    fig_width: 5
    
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Abstract

Transposon insertion sequencing (Tn-Seq) is a high-throughput technique to generate and culture a large random collection of genetically perturbed bacteria, followed by sequencing to measure the frequency of each perturbation in the culture. Tn-Seq is used for the identification of essential genes by utilizing the fact that mutants carrying insertions in such genes are expected to be greatly depleted in the growth culture. Here we present FiTnEss (Finding Tn-Seq Essential Genes) - a novel statistical method to identify gene essentiality using Tn-Seq data. The method contains only two global parameters that are estimated from the data. It is robust and has greater power to detect essential genes than TRANSIT, the leading existing method. We implemented FiTnEss on 9 strains of Pseudomonas aeruginosa under 5 biological conditions, and successfully characterized its core essential genome, validated by single-gene deletion experiments. A Bioconductor package for FiTnEss is under development. 

```{r, dev='CairoPDF',echo=FALSE}
library(FiTnEss)
library()
```

```{r, dev='CairoPDF'}
library(FiTnEss)
```


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.


Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
